---
title: "Experience"
---
I have spent multiple seasons conducting field work, both in Michigan's Upper Peninsula and in central Northern Idaho. 

## Marquette, Michigan

As an Invasive Species Field Technician for the Marquette County Conservation District, I worked to protect vital ecosystems in Michigan’s Upper Peninsula by managing invasive plant populations across federal, state, and private lands. I conducted extensive surveys, both on foot and by vehicle, covering diverse landscapes like the Hiawatha National Forest, Pictured Rocks National Lakeshore, and Seney National Wildlife Refuge. 

Using ArcGIS Field Maps, I accurately mapped invasive species occurrences in the Lake to Lake CISMA area, providing essential data to support local conservation efforts. I developed and executed self-directed daily plans, coordinating with field crews to ensure efficient and effective plant removal and habitat restoration. 

Notably, I contributed to habitat restoration efforts for the federally threatened Dwarf lake iris (Iris lacustris), reinforcing my commitment to preserving biodiversity. My role also involved continual learning and professional development, including attending regional training and field trips through the Michigan Invasive Species Coalition.

```{r fig.cap='Marquette County Conservation District', echo=FALSE}
htmltools::tags$iframe(title = "Field Work Photos", src = "mccdcarousel.html", frameborder = "0", width = "100%", height="450")
```

## McCall, Idaho

As a Botany Technician Intern with the Payette National Forest, I led and participated in extended field survey trips, working closely with a small team to conduct surveys that support sustainable land management. My role involved conducting rare and sensitive plant surveys to assess potential impacts of management activities, such as timber sales, hazardous fuel reduction, and road decommissioning projects. I documented understory and overstory plant species, using dichotomous keys and USDA plant codes to build accurate species inventories, and I also collected and prepared herbarium specimens for long-term reference.

I contributed to the conservation of sensitive species, including whitebark pine, by gathering critical spatial and statistical data with ArcGIS Field Maps, and I played an active role in developing a standardized data collection protocol for whitebark pine in collaboration with the USFS Region 4 Ecologist and Silviculturist, as well as the Rocky Mountain Research Station. Through this role, I honed my plant identification and field survey skills, while supporting meaningful conservation and habitat management work within the National Forest system.

```{r fig.cap='Payette National Forest', echo=FALSE}
htmltools::tags$iframe(title = "Field Work Photos", src = "pnfcarousel.html", frameborder = "0", width = "100%", height="450")
```
