---
title: "Experience"
---
I have spent multiple seasons conducting field work, in Michigan's Upper Peninsula, in central Northern Idaho, and on the west coast of the United States. 

## Ashland, Oregon

I worked for the National Park Service's Klamath Inventory and Monitoring Network (KLMN) based out of Southern Oregon University in Ashland, Oregon. As a vegetation monitoring technician, I collected data on and remonumented long-term monitoring plots. My crew and I navigated to pre-determined plots at Whiskeytown National Recreation Area and Lassen Volcanic National Park in northern California. We collected data on 1000^2^m plots, including-

:::::: columns
::: {.column width="45%"}
-   Species Presence or Absence
-   Tree and Snag Diameter and Density
-   Tree Crown Position
-   Shrub Density
-   Photo Plots
-   Tree Seedling Density
-   Tree and Shrub Mortality
-   Woody Debris Size and Decay Class
:::

::: {.column width="10%"}
<!-- empty column to create gap -->
:::

::: {.column width="45%"}
-   Canopy Height
-   Fuels
-   Disturbance
-   Soil Properties
-   Elevation
-   Slope
-   Aspect
-   Vegetation Type
:::
::::::

This data is used for a variety of projects from the KLMN, including reports on park health and other external publications. We visit plots once every three years, allowing for the monitoring of trends in vegetation composition and vegetation structure and function (including parameters affecting wildlife habitat, fire behavior, and stand dynamics), while still maintaining sensitivity to detect non-linear shifts in vegetation.

```{r fig.cap='Lassen Volcanic National Park and Whiskeytown National Recreation Area', echo=FALSE}
htmltools::tags$iframe(title = "Field Work Photos", src = "pnfcarousel.html", frameborder = "0", width = "100%", height="450")
```

## McCall, Idaho

As a Botany Technician Intern with the Payette National Forest, I led and participated in extended field survey trips, working closely with a small team to conduct surveys that support sustainable land management. My role involved conducting threatened and endangered species (TESP) surveys to assess potential impacts of management activities, such as timber sales, hazardous fuel reduction, and road decommissioning projects. I documented understory and overstory plant species, using dichotomous keys and USDA plant codes to build accurate species inventories, and I also collected, prepared, and mounted herbarium specimens for long-term reference.

I contributed to the conservation of sensitive species, including whitebark pine, by gathering critical spatial and statistical data with ArcGIS Field Maps, and I played an active role in developing a standardized data collection protocol for whitebark pine in collaboration with the USFS Region 4 Ecologist and Silviculturist, as well as the Rocky Mountain Research Station. Through this role, I honed my plant identification and field survey skills, while supporting meaningful conservation and habitat management work within the National Forest system.

```{r fig.cap='Payette National Forest', echo=FALSE}
htmltools::tags$iframe(title = "Field Work Photos", src = "pnfcarousel.html", frameborder = "0", width = "100%", height="450")
```

## Marquette, Michigan

As an Invasive Species Field Technician for the Marquette County Conservation District, I worked to protect vital ecosystems in Michigan’s Upper Peninsula by managing invasive plant populations across federal, state, and private lands. I conducted extensive surveys, both on foot and by vehicle, covering diverse landscapes like the Hiawatha National Forest, Pictured Rocks National Lakeshore, and Seney National Wildlife Refuge. 

Using ArcGIS Field Maps, I mapped invasive species occurrences in the Lake to Lake CISMA area, providing essential data to support local conservation efforts and inform future management strategies. I developed and executed self-directed daily plans, coordinating with field crews to ensure efficient and effective plant removal and habitat restoration. 

During my time with the Marquette County Conservation District, I contributed to habitat restoration efforts for the federally threatened Dwarf lake iris (Iris lacustris), reinforcing my commitment to preserving biodiversity. My role also involved continual learning and professional development, including attending regional CISMA training for the identification of Himalayan Balsam and European Frog Bit, as well as the 2023 Michigan Invasive Species Coalition summer field trip hosted by Lake to Lake CISMA.

```{r fig.cap='Marquette County Conservation District', echo=FALSE}
htmltools::tags$iframe(title = "Field Work Photos", src = "mccdcarousel.html", frameborder = "0", width = "100%", height="450")
```